Supplementary material for "Hack Weeks as a model for Data Science Education and Collaboration"

### 2018-04-13 supplementary_material.tex
Added 300ppi pdf version of hack spectrum, changed ref in intro, fixed typo in supplementary materials

Since human decision makers also routinely overestimate their ability to forecast future performance of a candidate and underestimate intrinsic variance during selection procedures, ~\cite{highhouse2008} it may be beneficial to set a fairly tolerant threshold for acceptance based on merit criteria, and select the cohort from this meritous pool via e.g.\ via an algorithm, imposing outside constraints on the selection based on the goals of the workshop.

>>>>

Since human decision makers also routinely overestimate their ability to forecast future performance of a candidate and underestimate intrinsic variance during selection procedures, ~\cite{highhouse2008} it may be beneficial to set a fairly tolerant threshold for acceptance based on merit criteria, and select the cohort from this meritorious pool via e.g.\ via an algorithm, imposing outside constraints on the selection based on the goals of the workshop.
